---
title: "fast-fires-explore"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("setup.R")
```

```{r echo=F, message=F, warning=F, error=F, include=F}
#########Bring in the data
setwd("C:/Users/mccoo/OneDrive/mcook/fast-fires/")
incidir <- "C:/Users/mccoo/OneDrive/mcook/thesis/data/"
datadir <- "C:/Users/mccoo/OneDrive/mcook/data/"

###ICS-209-PLUS table 1999-2018
inci209 <- read.csv(paste(incidir, "data_raw/tables/ics209-plus-wf_incidents_1999to2018.csv", sep=""))

###BUPR summary for events
events <- st_read("data/events/event_polys_albers_conus_w_eco_lc_bupr_proj.gpkg") 
events <- events %>%
   mutate(ignition_date = as.Date(ignition_date, "%Y-%m-%d"),
          last_date = as.Date(last_date, "%Y-%m-%d"),
          max_growth_date = as.Date(max_growth_date, "%Y-%m-%d"))
   
# daily <- st_read(
#    paste(data,
#          "FIRED/data/2020/edit/final/daily_polys_albers_conus_w_eco_lc.gpkg", sep="")) %>%
#    mutate(date = as.Date(date, "%Y-%m-%d"),
#           ignition_date = as.Date(ignition_date, "%Y-%m-%d"),
#           last_date = as.Date(last_date, "%Y-%m-%d"),
#           max_growth_date = as.Date(max_growth_date, "%Y-%m-%d"))

###Bring in the linked dataset
ics.fired <- st_read(
 paste(
  incidir, "data_mod/joins/new/event_polys_inci209_linked_2001to2018.gpkg", sep=""))

###Bring in the NIFC perims
nifc <- st_read("data/nifc/public_nifc_perims.gpkg")

###Bring in MTBS perims
mtbs <- st_read(paste(datadir, "mtbs/mtbs_perims_DD/mtbs_perims_DD.gpkg", sep="")) %>% mutate(
  Incid_Year = lubridate::year(Ig_Date)
) %>% filter(Incid_Year>=2000 & Incid_Year<=2020)

##Bring in CONUS shape
conus <- st_read(paste(datadir, "boundaries/political/TIGER/tl_2019_conus_state_albers.gpkg", sep=""))

###Bring in the ztrax
ztrax <- st_read("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/ztrax/extract/zasmt_fast_fires_extract.shp")%>%
   st_transform(st_crs(mtbs))

```

# First look at fast fires in ICS-209-PLUS only

```{r}
######Observed fast fires break and number of homes threatened, damaged, destroyed
ffInci <- inci209 %>% mutate(WF_MAX_FSR_HA = WF_MAX_FSR*0.404686) %>% filter(
 WF_MAX_FSR_HA >= 1620
)

ffTemp <- ff%>%filter(!is.na(STR_THREATENED_MAX))
inciTemp <- inci209%>%filter(!is.na(STR_THREATENED_MAX))

###Summarize number of threatened, damaged, destroyed structures by fast fires
paste("Total Structures Threatened: ", comma(sum(ffTemp$STR_THREATENED_MAX)), sep="")
paste("Total Structures Damaged: ", comma(sum(ff$STR_DAMAGED_TOTAL)), sep="")
paste("Total Structures Destroyed: ", comma(sum(ff$STR_DESTROYED_TOTAL)), sep="")
###Percent of homes threatened, damaged, destroyed
paste("Percent of Structures Threatened: ",
      sum(ffTemp$STR_THREATENED_MAX)/sum(inciTemp$STR_THREATENED_MAX)*100,
      sep="")
paste("Percent of Structures Damaged: ", 
      sum(ff$STR_DAMAGED_TOTAL)/sum(inci209$STR_DAMAGED_TOTAL)*100,
      sep="")
paste("Percent of Structures Destroyed: ", 
      sum(ff$STR_DESTROYED_TOTAL)/sum(inci209$STR_DESTROYED_TOTAL)*100,
      sep="")
#####Create subset of non-null suppression costs
ffTemp <- ff %>% filter(!is.na(PROJECTED_FINAL_IM_COST))
paste("Total Suppression Costs: ",
      comma(sum(ffTemp$PROJECTED_FINAL_IM_COST)), sep="")
```


# Next, summarize within the linked 209s-FIRED data

```{r}
setwd("C:/Users/mccoo/OneDrive/mcook/thesis/")
link <- st_read("data/data_mod/joins/new/event_polys_inci209_linked_2001to2018.gpkg")

link <- link %>% mutate(
   #Set factors for cause
   CAUSE = as.factor(CAUSE),
   FOD_CAUSE = as.factor(FOD_CAUSE),
   FOD_CAUSE_NUM = as.factor(FOD_CAUSE_NUM),
   max_growth_ha = max_growth_km2*100
)

summary(link$CAUSE)

link_fast <- link %>% filter(max_growth_ha>=1620)

summary(link_fast$CAUSE)
```


# Subset to fast fires (max daily growth > 1620ha)

```{r}
###Remove events that occurred prodominantly in cropland landcover
events <- events %>% filter(lc_name != "Croplands")

###Isolate fast fires
ffEvt <- events %>% mutate(max_growth_ha = max_growth_km2*100) %>% filter(max_growth_ha >= 1620)

###Get the top 100 fastest fires
ffEvt_top100 <- top_n(ffEvt, 100, max_growth_ha)
#And for the linked 209-FIRED data
ffEvt_linked <- ics.fired %>% filter(id %in% ffEvt$id)
#And see which of the top 100 have a link
ffEvt_linked100 <- ics.fired %>% filter(id %in% ffEvt_top100$id)
###Write out the top 100 events
# st_write(ffEvt_top100, "C:/Users/mccoo/OneDrive/mcook/fast-fires/data/fired_events_top100_fastest.gpkg")
# st_write(top100_link, "C:/Users/mccoo/OneDrive/mcook/fast-fires/data/fired_events_LINKED_top100_fastest.gpkg")

##################################################################
###Print some statistics of the fast fires subset
print("~~~~~~~~~~~BURNED AREA~~~~~~~~~~~~~")
summary(ffEvt_top100$max_growth_km2)
paste("% of total burned area: ",
      sum(ffEvt$total_area_km2)/sum(events$total_area_km2)*100, sep="")
print("~~~~~~~~~~~BUPR~~~~~~~~~~~~~")
paste("Number of exposed properties: ", sum(ffEvt$bupr_sum), sep="")
paste("Number of exposed properties 1km: ", sum(ffEvt$bupr_sum_1km), sep="")
paste("Number of exposed properties 4km: ", sum(ffEvt$bupr_sum_4km), sep="")
###Compare with total BUPR
paste("% of total BUPR in perimeters: ",
      sum(ffEvt$bupr_sum)/sum(events$bupr_sum)*100, sep="")
paste("% of total BUPR within 1km: ",
      sum(ffEvt$bupr_sum_1km)/sum(events$bupr_sum_1km)*100, sep="")

###Spatial map of top 100
ggplot()+
   geom_sf(data=conus)+
   geom_sf(data=ffEvt_top100)
```

# Daily Growth Plots

```{r}
###MTBS
hayman_fire_mtbs <- mtbs %>%
   filter(Event_ID == 'CO3922010528720020608')

###FIRED
hayman_fire_evt <- events %>% filter(id==6161)

###Grab some info for the plot
burn_year <- '2002'
ignition_date <- hayman_fire_evt$ignition_date
igngition_day <- hayman_fire_evt$ignition_day

###Get the annual burn date raster
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", burn_year, "/", sep="")

###Find ranges and set up plot
# proj <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=1,1,-1,0,0,0,0 +units=m +no_defs"
modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', burn_year, '.tif', sep=""))) %>%
   raster::crop(hayman_fire_mtbs) %>%
   raster::mask(hayman_fire_mtbs)

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
start <- as.numeric(range[1])
breaks <- abs(range[1]-range[2])

#Update raster values to get "day since ignition"
modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

# A function to plot our raster data
hayman_fire_map <- rasterVis::levelplot(modis_burn_dates,
                     par.settings = list(layout.heights=list(xlab.key.padding=1),
                                         axis.line = list(col = "transparent"),
                                         strip.background = list(col = 'transparent'),
                                         strip.border = list(col = 'transparent')),
                     margin=FALSE, region = TRUE,
                     xlab = list(label = 'Days Since Ignition', cex = 1.5), 
                     main = 'Hayman Fire, CO, 2002',
                     scales = list(draw = FALSE),
                     ylab=NULL,
                     col.regions = colorRampPalette(brewer.pal(11, 'YlOrRd'))(breaks),
                     colorkey = list(col = colorRampPalette(brewer.pal(11, 'YlOrRd'))(breaks),
                                     space="bottom")) +
  latticeExtra::layer(sp.polygons(as(hayman_fire_mtbs, 'Spatial'), lwd = 1, scales=list(axes=FALSE))) +
  latticeExtra::layer(sp.points(as(ztrax_ext, 'Spatial'), pch = 16, size = 1, col = 'black'))

hayman_fire_map
```

```{r}
###MTBS
hayman_fire_mtbs <- mtbs %>%
   filter(Event_ID == 'CO3922010528720020608')
###Filter the ztrax
ztrax_ext <- ztrax %>% filter(YearBuilt<=2002) %>%
   st_intersection(., hayman_fire_mtbs)
###########GGPLOT2 version
###Grab some info for the plot
burn_year <- '2002'
ignition_date <- hayman_fire_evt$ignition_date
igngition_day <- hayman_fire_evt$ignition_day

###Get the annual burn date raster
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", burn_year, "/", sep="")

###Find ranges and set up plot
# proj <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=1,1,-1,0,0,0,0 +units=m +no_defs"
modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', burn_year, '.tif', sep=""))) %>%
   raster::crop(hayman_fire_mtbs) %>%
   raster::mask(hayman_fire_mtbs)

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
start <- as.numeric(range[1])
breaks <- abs(range[1]-range[2])

#Update raster values to get "day since ignition"
modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

#Extract as DF
modis_burn_dates <- as.data.frame(modis_burn_dates, xy = TRUE)
#Plot
ggplot() +
   geom_raster(data = modis_burn_dates , aes(x = x, y = y, fill=annual_burndate_y2002)) +
   scico::scale_fill_scico(palette = "lajolla", na.value="white",
                           breaks=seq(0,35,5), labels=c(0,5,10,15,20,25,30,35))+
   geom_sf(data=hayman_fire_mtbs, fill="transparent", size=0.65)+
   geom_sf(data=ztrax_ext, color="black", size=1)+
   labs(title="Hayman Fire, CO (2002)",
        fill="Days Since Ignition")+
   theme_void()+
   theme(legend.position="bottom",
         plot.title = element_text(hjust = 0.5))+
   guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5,
                                 barwidth = 12, barheight = 0.5,
                                 ticks=FALSE, draw.llim=FALSE))+
   coord_sf()
```


```{r}
###ZTRAX
ztrax_ext <- ztrax %>% filter(YearBuilt<=2017)

###MTBS
tubbs_fire_mtbs <- mtbs %>%
  filter(Event_ID == 'CA3859812261820171009')

#FIRED
tubbs_fire_evt <- events %>% filter(id==117157)

###Params
year <- '2017'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

###Tubbs fire example
modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
  raster::crop(tubbs_fire_mtbs) %>%
  raster::mask(tubbs_fire_mtbs)

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
start <- range[1]
breaks <- abs(range[1]-range[2])

#Update cells to be "days since ignition
modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

# A function to plot our raster data
tubbs_fire_map <- rasterVis::levelplot(modis_burn_dates,
                     par.settings = list(layout.heights=list(xlab.key.padding=1),
                                         axis.line = list(col = "transparent"),
                                         strip.background = list(col = 'transparent'),
                                         strip.border = list(col = 'transparent')),
                     margin=FALSE, region = TRUE,
                     xlab = list(label = 'Days Since Ignition', cex = 1.5), 
                     main = 'Tubbs Fire, CA, 2017',
                     scales = list(draw = FALSE),
                     ylab=NULL,
                     col.regions = colorRampPalette(brewer.pal(11, 'YlOrRd'))(breaks),
                     colorkey = list(col = colorRampPalette(brewer.pal(11, 'YlOrRd'))(breaks),
                                     space="bottom")) +
  latticeExtra::layer(sp.polygons(as(tubbs_fire_mtbs, 'Spatial'), lwd = 1, scales=list(axes=FALSE))) +
  latticeExtra::layer(sp.points(as(ztrax_ext, 'Spatial'), pch = 16, size = 1, col = 'black'))

tubbs_fire_map
```

```{r}
camp_fire <- inci209 %>%
  filter(INCIDENT_ID == "2018_9220077_CAMP")
# Create the spatial
camp_fire_pt <- camp_fire %>%
  mutate(POO_LONGITUDE = ifelse(is.na(POO_LONGITUDE),0,as.numeric(POO_LONGITUDE)),
         POO_LATITUDE = ifelse(is.na(POO_LATITUDE),0,as.numeric(POO_LATITUDE))) %>%
  st_as_sf(., coords = c("POO_LONGITUDE", "POO_LATITUDE"),
                       crs = st_crs(conus)) %>%
  st_transform(crs = st_crs(conus))

#FIRED
camp_fire_evt <- events%>%filter(id==124486)
ignition_date <- camp_fire_evt$ignition_date
last_date <- camp_fire_evt$last_date

#MTBS
camp_fire_mtbs <- mtbs %>%
   filter(Event_ID == 'CA3982012144020181108')
   
year <- '2018'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

# proj <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=1,1,-1,0,0,0,0 +units=m +no_defs"
modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(camp_fire_mtbs) %>%
   raster::mask(camp_fire_mtbs)
plot(modis_burn_dates)

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])
end <- as.numeric(range[2])

modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

##Handle possible error dates
modis_burn_dates[modis_burn_dates>31] <- NA

# A function to plot our raster data
camp_fire_map <- rasterVis::levelplot(modis_burn_dates,
                     par.settings = list(layout.heights=list(xlab.key.padding=1),
                                         axis.line = list(col = "transparent"),
                                         strip.background = list(col = 'transparent'),
                                         strip.border = list(col = 'transparent')),
                     margin=FALSE, region = TRUE,
                     xlab = list(label = 'Days Since Ignition', cex = 1.5), 
                     main = 'Camp Fire, CA, 2018',
                     scales = list(draw = FALSE),
                     ylab=NULL,
                     col.regions = colorRampPalette(brewer.pal(11, 'YlOrRd'))(breaks),
                     colorkey = list(col = colorRampPalette(brewer.pal(11, 'YlOrRd'))(breaks),
                                     space="bottom")) +
  latticeExtra::layer(sp.polygons(as(camp_fire_mtbs, 'Spatial'), lwd = 1, scales=list(axes=FALSE)))

camp_fire_map
```

```{r}
#FIRED
woolsey_fire_evt <- events%>%filter(id==124525)
ignition_date <- camp_fire_evt$ignition_date
last_date <- camp_fire_evt$last_date

#MTBS
woolsey_fire_mtbs <- mtbs %>%
   filter(Event_ID == 'CA3424011870020181108')
   
year <- '2018'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

# proj <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=1,1,-1,0,0,0,0 +units=m +no_defs"
modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(woolsey_fire_mtbs) %>%
   raster::mask(woolsey_fire_mtbs)
plot(modis_burn_dates)

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])
end <- as.numeric(range[2])

modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

##Handle possible error dates
# modis_burn_dates[modis_burn_dates>31] <- NA

# A function to plot our raster data
woolsey_fire_map <- rasterVis::levelplot(modis_burn_dates,
                     par.settings = list(layout.heights=list(xlab.key.padding=1),
                                         axis.line = list(col = "transparent"),
                                         strip.background = list(col = 'transparent'),
                                         strip.border = list(col = 'transparent')),
                     margin=FALSE, region = TRUE,
                     xlab = list(label = 'Days Since Ignition', cex = 1.5), 
                     main = 'Woolsey Fire, CA, 2018',
                     scales = list(draw = FALSE),
                     ylab=NULL,
                     col.regions = colorRampPalette(brewer.pal(11, 'YlOrRd'))(breaks),
                     colorkey = list(col = colorRampPalette(brewer.pal(11, 'YlOrRd'))(breaks),
                                     space="bottom")) +
  latticeExtra::layer(sp.polygons(as(woolsey_fire_mtbs, 'Spatial'), lwd = 1, scales=list(axes=FALSE)))

woolsey_fire_map
```

```{r}
oks_fire <- inci209 %>%
  filter(INCIDENT_ID == "2017_7145623_OKS - STARBUCK")
# Create the spatial
oks_fire_pt <- oks_fire %>%
  mutate(POO_LONGITUDE = ifelse(is.na(POO_LONGITUDE),0,as.numeric(POO_LONGITUDE)),
         POO_LATITUDE = ifelse(is.na(POO_LATITUDE),0,as.numeric(POO_LATITUDE))) %>%
  st_as_sf(., coords = c("POO_LONGITUDE", "POO_LATITUDE"),
                       crs = st_crs(conus)) %>%
  st_transform(crs = st_crs(conus))

oks_fire_mtbs <- mtbs %>%
   filter(Event_ID == 'OK3677410017520170307')

#FIRED
oks_fire_evt <- events%>%filter(id==112198)

year <- '2017'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

###Hayman fire example
# proj <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=1,1,-1,0,0,0,0 +units=m +no_defs"
modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(oks_fire_mtbs) %>%
   raster::mask(oks_fire_mtbs)

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])

modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

# A function to plot our raster data
oks_fire_map <- rasterVis::levelplot(modis_burn_dates,
                     par.settings = list(layout.heights=list(xlab.key.padding=1),
                                         axis.line = list(col = "transparent"),
                                         strip.background = list(col = 'transparent'),
                                         strip.border = list(col = 'transparent')),
                     margin=FALSE, region = TRUE,
                     xlab = list(label = 'Days Since Ignition', cex = 1.5), 
                     main = 'OKS-Starbuck, OK, 2017',
                     scales = list(draw = FALSE),
                     ylab=NULL,
                     col.regions = colorRampPalette(brewer.pal(breaks, 'YlOrRd')),
                     colorkey = list(col = colorRampPalette(brewer.pal(breaks, 'YlOrRd')),
                                     space="bottom")) +
  latticeExtra::layer(sp.polygons(as(oks_fire_mtbs, 'Spatial'), lwd = 1, scales=list(axes=FALSE)))

oks_fire_map
```

```{r}
king_fire <- inci209 %>%
  filter(INCIDENT_ID == "2014_983669_KING")
# Create the spatial
king_fire_pt <- oks_fire %>%
  mutate(POO_LONGITUDE = ifelse(is.na(POO_LONGITUDE),0,as.numeric(POO_LONGITUDE)),
         POO_LATITUDE = ifelse(is.na(POO_LATITUDE),0,as.numeric(POO_LATITUDE))) %>%
  st_as_sf(., coords = c("POO_LONGITUDE", "POO_LATITUDE"),
                       crs = st_crs(conus)) %>%
  st_transform(crs = st_crs(conus))

king_fire_mtbs <- mtbs %>%
   filter(Event_ID == 'CA3878212060420140913')

#FIRED
king_fire_evt <- events%>%filter(id==95950)

year <- '2014'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

###Hayman fire example
# proj <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=1,1,-1,0,0,0,0 +units=m +no_defs"
modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(king_fire_mtbs) %>%
   raster::mask(king_fire_mtbs)

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])

modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

# A function to plot our raster data
king_fire_map <- rasterVis::levelplot(modis_burn_dates,
                     par.settings = list(layout.heights=list(xlab.key.padding=1),
                                         axis.line = list(col = "transparent"),
                                         strip.background = list(col = 'transparent'),
                                         strip.border = list(col = 'transparent')),
                     margin=FALSE, region = TRUE,
                     xlab = list(label = 'Days Since Ignition', cex = 1.5), 
                     main = 'King Fire, CA, 2014',
                     scales = list(draw = FALSE),
                     ylab=NULL,
                     col.regions = colorRampPalette(brewer.pal(breaks, 'YlOrRd')),
                     colorkey = list(col = colorRampPalette(brewer.pal(breaks, 'YlOrRd')),
                                     space="bottom")) +
  latticeExtra::layer(sp.polygons(as(king_fire_mtbs, 'Spatial'), lwd = 1, scales=list(axes=FALSE)))

king_fire_map
```

```{r}
witch_fire_mtbs <- mtbs %>%
   filter(Event_ID == 'CA3307911676620071021')

dissolve <- st_union(witch_fire_mtbs)%>%st_sf()

#FIRED
witch_fire_evt <- events%>%filter(id==46183)

year <- '2007'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

###Hayman fire example
# proj <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=1,1,-1,0,0,0,0 +units=m +no_defs"
modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(witch_fire_mtbs) %>%
   raster::mask(witch_fire_mtbs)

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])

modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

# A function to plot our raster data
witch_fire_map <- rasterVis::levelplot(modis_burn_dates,
                     par.settings = list(layout.heights=list(xlab.key.padding=1),
                                         axis.line = list(col = "transparent"),
                                         strip.background = list(col = 'transparent'),
                                         strip.border = list(col = 'transparent')),
                     margin=FALSE, region = TRUE,
                     xlab = list(label = 'Days Since Ignition', cex = 1.5), 
                     main = 'Witch-Poomacha Fire, CA, 2007',
                     scales = list(draw = FALSE),
                     ylab=NULL,
                     col.regions = colorRampPalette(brewer.pal(breaks, 'YlOrRd')),
                     colorkey = list(col = colorRampPalette(brewer.pal(breaks, 'YlOrRd')),
                                     space="bottom")) +
  latticeExtra::layer(sp.polygons(as(witch_fire_mtbs, 'Spatial'), lwd = 1, scales=list(axes=FALSE)))

witch_fire_map
```


```{r}
cold_springs_cmplx <- nifc %>%
   filter(LocalIncid == "000594" |
          LocalIncid == "200130" |
          LocalIncid == "002144") %>%
   st_transform(crs = st_crs(mtbs))

dissolve <- st_union(cold_springs_cmplx)%>%st_sf()

year <- '2020'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(dissolve) %>%
   raster::mask(dissolve)
plot(modis_burn_dates)

modis_burn_dates[modis_burn_dates<245] <- NA

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])

modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

# A function to plot our raster data
cold_springs_cmplx_map <- rasterVis::levelplot(modis_burn_dates,
                     par.settings = list(layout.heights=list(xlab.key.padding=1),
                                         axis.line = list(col = "transparent"),
                                         strip.background = list(col = 'transparent'),
                                         strip.border = list(col = 'transparent')),
                     margin=FALSE, region = TRUE,
                     xlab = list(label = 'Days Since Ignition', cex = 1.5), 
                     main = 'Cold Springs Complex, WA, 2020',
                     scales = list(draw = FALSE),
                     ylab=NULL,
                     col.regions = colorRampPalette(brewer.pal(breaks, 'YlOrRd'))(breaks),
                     colorkey = list(col = colorRampPalette(brewer.pal(breaks, 'YlOrRd'))(breaks),
                                     space="bottom")) +
  latticeExtra::layer(sp.polygons(as(cold_springs_cmplx, 'Spatial'), lwd = 1, scales=list(axes=FALSE)))

cold_springs_cmplx_map
```

```{r}
claremont_bear <- nifc %>%
   filter(LocalIncid == "001308") %>%
   st_transform(crs = st_crs(mtbs))

year <- '2020'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(claremont_bear) %>%
   raster::mask(claremont_bear)

##Handle possible error dates
modis_burn_dates[modis_burn_dates>279] <- NA

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])

modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])

# A function to plot our raster data
claremont_bear_map <- rasterVis::levelplot(modis_burn_dates,
                     par.settings = list(layout.heights=list(xlab.key.padding=1),
                                         axis.line = list(col = "transparent"),
                                         strip.background = list(col = 'transparent'),
                                         strip.border = list(col = 'transparent')),
                     margin=FALSE, region = TRUE,
                     xlab = list(label = 'Days Since Igntiion', cex = 1.5), 
                     main = 'Claremont-Bear, CA, 2020',
                     scales = list(draw = FALSE),
                     ylab=NULL,
                     col.regions = colorRampPalette(brewer.pal(breaks, 'YlOrRd')),
                     colorkey = list(col = colorRampPalette(brewer.pal(breaks, 'YlOrRd')),
                                     space="bottom")) +
   latticeExtra::layer(sp.polygons(as(claremont_bear, 'Spatial'), lwd = 1, scales=list(axes=TRUE))) 

claremont_bear_map

```

```{r}
august_cmplx <- nifc %>%
   filter(LocalIncid == "000753") %>%
   st_transform(crs = st_crs(mtbs))

year <- '2020'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(august_cmplx) %>%
   raster::mask(august_cmplx)

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])

modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])

# A function to plot our raster data
august_cmplx_map <- rasterVis::levelplot(modis_burn_dates,
                     par.settings = list(layout.heights=list(xlab.key.padding=1),
                                         axis.line = list(col = "transparent"),
                                         strip.background = list(col = 'transparent'),
                                         strip.border = list(col = 'transparent')),
                     margin=FALSE, region = TRUE,
                     xlab = list(label = 'Days Since Igntiion', cex = 1.5), 
                     main = 'August Complex, CA, 2020',
                     scales = list(draw = FALSE),
                     ylab=NULL,
                     col.regions = colorRampPalette(brewer.pal(breaks, 'YlOrRd')),
                     colorkey = list(col = colorRampPalette(brewer.pal(breaks, 'YlOrRd')),
                                     space="bottom")) +
   latticeExtra::layer(sp.polygons(as(august_cmplx, 'Spatial'), lwd = 1, scales=list(axes=TRUE))) 

august_cmplx_map

```

```{r}
###Merge the spatial data and save
boundaries <- st_combine(camp_fire_mtbs, witch_fire_mtbs)
```

# Panel figure

```{r, fig.width=10, fig.height=6, warning=False}
grid.arrange(hayman_fire_map, witch_fire_map, oks_fire_map, 
             camp_fire_map, august_cmplx_map, cold_springs_cmplx_map,
             ncol=3, nrow=2)

# library(latticeExtra)
# c(camp_fire_map, hayman_fire_map, tubbs_fire_map, 
#   oks_fire_map, cold_springs_cmplx_map, claremont_bear_map)

# cowplot::plot_grid(camp_fire_map, hayman_fire_map, tubbs_fire_map, 
#                    oks_fire_map, cold_springs_cmplx_map, claremont_bear_map,
#                    align = "v", ncol = 3, rel_heights = c(1/4, 1/4, 1/4))
```

```{r, fig.width=10, fig.height=9, warning=False}
grid.arrange(hayman_fire_map, witch_fire_map, oks_fire_map, 
             tubbs_fire_map, camp_fire_map, woolsey_fire_map,
             august_cmplx_map, cold_springs_cmplx_map, claremont_bear_map,
             ncol=3, nrow=3)
```

# Plot BUPR sum through burn days

## Here, we will test various methods for temporal autocorrelation between burn area and housing density. We will also test the relationship between maximum growth and maximum housing density.

```{r, fig.caption="Test"}
###Create daily fired subset
#####Let's take an example fire, the Rim Fire in CA
ex <- daily %>% filter(id==57206) %>%
   #daily hectares
   mutate(daily_area_ha = daily_area_km2*100)

###Create a simple time-series plot
p1 <- ggplot(ex)+
   geom_line(aes(date, daily_area_km2), na.rm=TRUE)+
   xlab("")+
   ylab("Daily Growth (km2)")+
   scale_x_date(breaks=date_breaks("5 days"),
                labels=date_format("%b %d"))+
   theme_light()
p2 <- ggplot(ex, aes(date, bupr_sum))+
   geom_bar(stat="identity")+
   xlab("Burn Date")+
   ylab("Built-up Property Records")+
   scale_x_date(breaks=date_breaks("5 days"),
                labels=date_format("%b %d"))+
   theme_light()

arr <- ggarrange(p1, p2, nrow = 2, ncol = 1)

annotate_figure(arr, top="Daily Burn Area and Property Density for the Rim Fire, CA")

```

