---
title: "fast-fires"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("setup.R")
```

Summary of Fast Fire impacts from the ICS-209-PLUS (1999-2020). 

First, we need to handle possible multiple entries due to the reporting nature for complex fires.

```{r include=F}
# Load the complex associations table
complex <- read_csv(paste0(icsdir,"/data/tabular/raw/wf-incidents/ics-plus_v2.0/
                           icsplus-wildfire/ics-plus-wf_complex_associations_1999to2020.csv"))
# Isolate non-complex fires
no.cmplx <- ics %>% 
 # Remove some known "problem fires"
 filter(INCIDENT_ID != "2017_7211255_REDWOOD VALLEY INCIDENT",
        INCIDENT_ID != "2017_7293073_REDWOOD VALLEY INCIDENT") %>%
 # Filter incidents with 0 acres
 filter(FINAL_ACRES!=0,
        # remove incidents found in the complex associations table
        !INCIDENT_ID %in% complex$MEMBER_INCIDENT_ID,
        # filter to fires where FPA-FOD shows 1 event or NULL
        FOD_FIRE_NUM==1 | is.na(FOD_FIRE_NUM))
# Isolate complex fires
cmplx <- ics %>%
 filter(INCIDENT_ID %in% complex$CPLX_INCIDENT_ID)
# bind to a temporary layer
ics <- bind_rows(no.cmplx,cmplx)
rm(no.cmplx,cmplx,complex)
```

Summary statistics from the ICS209-PLUS:

```{r}
# Observed fast fires break and number of homes threatened, damaged, destroyed
ics.fast <- ics %>% 
 mutate(WF_MAX_FSR_HA = WF_MAX_FSR*0.404686) %>% 
 filter(WF_MAX_FSR_HA >= 1620) %>%
 filter(START_YEAR >= 2000)

# Summarize number of threatened, damaged, destroyed structures by fast fires from the 209s
print("ICS-209-PLUS 1999-2020 Fast Fires, Structural Impacts: ")
print("~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~")
paste0("Total Structures Threatened: ", scales::comma(sum(ics.fast$STR_THREATENED_MAX, na.rm=TRUE)))
paste0("Total Structures Damaged: ", scales::comma(sum(ics.fast$STR_DAMAGED_TOTAL, na.rm=TRUE)))
paste0("Total Structures Destroyed: ", scales::comma(sum(ics.fast$STR_DESTROYED_TOTAL, na.rm=TRUE)))
paste0("Total Residential Structures Destroyed: ",scales::comma(sum(ics.fast$STR_DESTROYED_RES_TOTAL, na.rm=TRUE)))
print("~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~")
# Percent of homes threatened, damaged, destroyed
paste0("Percent of Structures Threatened: ",
      sum(ics.fast$STR_THREATENED_MAX, na.rm=T)/sum(ics$STR_THREATENED_MAX, na.rm=T)*100)
paste0("Percent of Structures Damaged: ", 
      sum(ics.fast$STR_DAMAGED_TOTAL, na.rm=T)/sum(ics$STR_DAMAGED_TOTAL, na.rm=T)*100)
paste0("Percent of Structures Destroyed: ", 
      sum(ics.fast$STR_DESTROYED_TOTAL, na.rm=T)/sum(ics$STR_DESTROYED_TOTAL, na.rm=T)*100)
paste0("Percent of Residential Structures Destroyed: ", 
      sum(ics.fast$STR_DESTROYED_RES_TOTAL, na.rm=T)/sum(ics$STR_DESTROYED_RES_TOTAL, na.rm=T)*100)
print("~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~")
paste0("Total Suppression Costs: ",scales::comma(sum(ics.fast$PROJECTED_FINAL_IM_COST, na.rm=T)))
paste0("Percent of Suppression Costs: ",
      scales::comma(sum(ics.fast$PROJECTED_FINAL_IM_COST, na.rm=T)/
                     sum(ics$PROJECTED_FINAL_IM_COST, na.rm=T)*100))
# Write out
st_write(ics.fast, "../../data/spatial/mod/ics209plus_conus_fast_2000to2020.gpkg", delete_dsn=T)
```

Subset FIRED events to fast fires (max daily growth > 1620ha). Exclude cropland systems.

```{r warning=F}

bupr <- read_csv("../../data/tabular/bupr_sums.csv") %>%
 dplyr::select(id,bupr_sum,bupr_sum1km,bupr_sum4km)

# Remove fired that occurred predominantly in cropland landcover
fired.fast <- fired %>% 
 dplyr::select(-c(bupr_sum,bupr_sum1k)) %>%
 filter(lc_name != "Croplands") %>%
 mutate(mx_grw_ha = mx_grw_km2*100) %>% 
 filter(mx_grw_ha >= 1620) %>%
 st_transform(st_crs(lambert.prj)) %>%
 # Join to BUPR summary
 left_join(bupr, by="id")

# Get the top 100 fastest fires in FIRED
fired.t100 <- top_n(fired.fast, 100, mx_grw_ha)
# Get the top 100 fastest fires in ICS-FIRED
ics.fired.t100 <- ics.fired %>%
 mutate(mx_grw_ha = mx_grw_km2*100,
        tot_ar_ha = tot_ar_km2*100) %>%
 filter(mx_grw_ha >= 1620) %>%
 top_n(., 100, mx_grw_ha) %>%
 st_transform(st_crs(lambert.prj))

# Write out the top 100 fires
st_write(fired.fast, "../../data/spatial/mod/conus_fast-fires_2001to2020.gpkg", delete_dsn=T)
st_write(fired.t100, "../../data/spatial/mod/fastest100_fired.gpkg", delete_dsn=T)
st_write(ics.fired.t100, "../../data/spatial/mod/fastest100_ics-fired.gpkg", delete_dsn=T)
```

```{r}
# Print some statistics of the fast fires subset
print("1.7% of fires in the FIRED database meet the fast fires threshold ...")
print("~~~~~~~~~~~Summary of Max Growth~~~~~~~~~~~~~")
summary(fired.fast$mx_grw_km2)
print("~~~~~~~~~~~BURNED AREA~~~~~~~~~~~~~")
paste0("% of total burned area: ",
      sum(fired.fast$tot_ar_km2)/sum(fired$tot_ar_km2)*100)
print("~~~~~~~~~~~BUPR~~~~~~~~~~~~~")
paste0("Number of exposed properties within perimeter: ", sum(fired.fast$bupr_sum,na.rm=T))
paste0("Number of exposed properties within 1km: ", sum(fired.fast$bupr_sum1k,na.rm=T))
paste0("Number of exposed properties within 4km: ", sum(fired.fast$bupr_sum4k,na.rm=T))
```

Figure 1. Spatial distribution of fast fires across CONUS. Top 100 fastest fires are highlighted by size/color.

```{r warning=F, message=F}

# Bring in cities and lakes
cities <- st_read(paste0(maindir,"/data/boundaries/political/USGS/USA_MajorCities.shp")) %>%
 st_transform(st_crs(lambert.prj)) %>%
 filter(NAME == "Denver")
lakes <- st_read(paste0(maindir,"/data/water/great_lakes.gpkg"))

# Spatial map of top 100
centroid1 <- st_centroid(fired.fast)
centroid2 <- st_centroid(fired.t100)
centroid3 <- st_centroid(ics.fired.t100)

f1 <- ggplot() + 
   geom_sf(data = states, lwd=0.7, color=alpha("gray20", 0.85), fill=alpha("white",0.75)) +
   geom_sf(data = states %>% st_buffer(1e5), color=NA, fill=NA) +
   geom_sf(data = centroid1, color=alpha("gray40", 1), size=0.3) +
   geom_sf(data = centroid2, aes(color=mx_grw_ha, size=mx_grw_ha)) +
   # geom_sf(data=cities, size=2.5, shape=18) +
   # geom_sf(data=lakes, color=NA, fill="grey75") +
   scale_color_viridis_c(trans="log", option="inferno", direction=-1,
                         breaks=c(20000,40000,80000,160000),
                         labels=c("20k","40k","80k","160k")) +
   labs(fill="", color="Max Single-Day Growth (ha/day)") +
   guides(color = guide_colourbar(direction = "horizontal", barwidth = 11, barheight = 0.60, 
                                  ticks=F, title.position = "top"),
          label.theme = element_text(angle = 0, size = 9),
          size="none") +
   theme_void() +
   theme(plot.margin = unit(c(0.0,0.0,0.0,0.0), "in"),
         plot.title = element_blank(),
         legend.title = element_text(angle = 0, size=10),
         legend.text = element_text(size=9),
         legend.position=c(0.23, 0.08)) +
   ggspatial::annotation_scale(location = "br", width_hint = 0.1,
                               pad_x = unit(0.2,"in"), pad_y = unit(0.2,"in"),
                               line_width = 0.5, text_pad = unit(0.15,"cm"),
                               height = unit(0.15,"cm")) +
   ggspatial::annotation_north_arrow(location = "br", which_north = "true",
                                     pad_x = unit(0.3,"in"), pad_y= unit(0.4,"in"),
                                     width = unit(0.8,"cm"), height = unit(0.8,"cm"),
                                     style = north_arrow_fancy_orienteering)
f1

# Save it out
ggsave(f1, file = "../../figures/Figure1_fastest_fires_conus.png",
       dpi = 300, bg="white") # adjust dpi accordingly

rm(f1,centroid1,centroid2,centroid3,cities,lakes)
```

Table 1. Top 20 fastest fires in CONUS (2000-2020)

Retrieve the ICS209-PLUS records for the top 20 fastest fires, where possible. Some fires identified in the top 100 fastest FIRED perimeters do not have a certain match in ICS209-PLUS. So, this list had to be quality controlled with some manual testing.

```{r}

# "2005_NV-LVD-000042_SOUTHERN NEVADA COMPLEX"

# INCIDENT_ID list for the top 20 fastest fires"
qc_list <- c("2020_COLD SPRINGS COMPLEX","2020_11850821_LNU LIGHTNING COMPLEX")
incid_list <- c("2017_7155675_NW OKLAHOMA COMPLEX", "2012_OR-VAD-000067_LONG DRAW", "2017_7161319_PERRYTON",
                "2016_4258135_ANDERSON CREEK FIRE", "2007_ID-TFD-002030_MURPHY COMPLEX",
                "2006_TX-TXS-066077_EAST AMARILLO COMPLEX","2018_9206799_MARTIN", "2007_UT-SWS-070312_MILFORD FLAT",
                "2008_TX-TXS-88071_GLASS FIRE", "2014_634805_BUZZARD COMPLEX", "2020_11843929_AUGUST COMPLEX",
                "2012_ID-TFD-000263_KINYON ROAD", "2015_2880290_SODA", "2018_9021840_RHEA",
                "2020_11865970_NORTH COMPLEX", "2003_CA-CNF-003056_CEDAR", "2011_TX-TXS-011088_COOPER MOUNTAIN RANCH",
                "2007_CA-MVU-010432_WITCH")

# Grab the ICS209-PLUS records
ics.t <- ics %>% filter(INCIDENT_ID %in% incid_list)

# Grab the "QC" fires
ics.t.a <- st_read(paste0(maindir,"/home-loss/data/spatial/mod/ics-fired_spatial_west_mod.gpkg")) %>%
 st_transform(st_crs(lambert.prj)) %>%
 filter(INCIDENT_ID %in% qc_list) %>%
 st_set_geometry(NULL) %>% as_tibble()

# Export the table of top 20 fastest fires (QCd)
ics.t %>%
 bind_rows(ics.t.a) %>%
 write_csv('../../data/tabular/fastest20_qc_table.csv')

rm(ics.t,ics.t.a,qc_list,incid_list,fired.t100,ics.fired.t100)
gc()
```

Figure 2. Case study, selection of fast fires from the top 100 with ZTRAX point locations and daily burned area.

Load the ZTRAX:

```{r}
ztrax <- st_read("../../data/spatial/mod/ztrax/extract/zasmt_fast_fires_extract.shp")%>%
 st_transform(st_crs(mtbs))
```

NW OKLAHOMA COMPLEX:

The fastest recorded fire in the database ...

```{r}
# MTBS footprint
nw_ok_complex_mtbs <- mtbs %>%
 filter(Event_ID %in% c("OK3671009983720170307",'OK3677410017520170307'))
# ZTRAX point locations
ztrax_ext <- ztrax %>% 
 filter(YearBuilt<=2017) %>%
 st_intersection(., nw_ok_complex_mtbs)

# Setup the burndate raster
year <- '2017'
fire_dir <- paste0(maindir,"/fast-fires/data/spatial/raw/burndate/",year,"/")
modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(nw_ok_complex_mtbs) %>%
   raster::mask(nw_ok_complex_mtbs)

# Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])
# Convert to days since ignition
modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)
# Extract as DF
modis_burn_dates <- as.data.frame(modis_burn_dates, xy = TRUE)
# Plot
nw_ok_complex_map <- ggplot() +
   geom_raster(data = modis_burn_dates , aes(x = x, y = y, fill=annual_burndate_y2017)) +
   scale_fill_fermenter(n.breaks=5, palette="Reds", na.value="white") +
   geom_sf(data=oks_fire_mtbs, fill="transparent", size=0.65)+
   geom_sf(data=ztrax_ext, color=alpha("black",0.3), size=0.85, shape=18, show.legend = TRUE)+
   labs(title="OKS-Starbuck Fire, OK (2017)",
        fill="Days Since Ignition")+
   theme_void()+
   theme(legend.position="bottom",
         plot.title = element_text(hjust = 0.5))+
   guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5,
                                 barwidth = 12, barheight = 0.5,
                                 ticks=FALSE, draw.llim=FALSE))+
   ggsn::scalebar(oks_fire_mtbs, dist = 10, st.size=2.5, height=0.01, 
                  dist_unit="km", model = 'WGS84', transform=TRUE)+
   coord_sf()
nw_ok_complex_map
```


```{r}

# North Complex fire data
north.mtbs <- mtbs %>% filter(Incid_Name=="NORTH COMPLEX")
north.fired <- fired.fast %>% filter(id==135490)

# Fire duration
startDate <- north.fired$ig_date
endDate <- north.fired$last_date

# Grab MODIS burned pixels/dates
year <- '2020'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")
modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(north.mtbs) %>%
   raster::mask(north.mtbs)

# Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])
end <- as.numeric(range[2])
modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

# Extract as DF
modis_burn_dates <- as.data.frame(modis_burn_dates, xy = TRUE) %>% na.omit()
# Plot
north.map <- ggplot() +
   geom_tile(data = modis_burn_dates , aes(x = x, y = y, fill=annual_burndate_y2020)) +
   # scico::scale_fill_scico(palette = "lajolla", na.value="white", alpha=0.9,
   #                         breaks=seq(0,35,5), labels=c(0,5,10,15,20,25,30,35))+
   # scale_fill_distiller(palette = 'YlOrRd', direction=-2, breaks=seq(0,35,5),
   #                      na.value="white")+
   scale_fill_fermenter(n.breaks=10, palette="Reds", na.value="white") +
   geom_sf(data=north.mtbs, fill="transparent", size=0.65)+
   # geom_sf(data=ztrax_ext, color=alpha("black",0.05), size=0.65, shape=18, show.legend = TRUE)+
   labs(title="North Complex, CA (2020)",
        fill="Days Since Ignition")+
   theme_void()+
   theme(legend.position="bottom",
         plot.title = element_text(hjust = 0.5))+
   guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5,
                                 barwidth = 12, barheight = 0.5,
                                 ticks=FALSE, draw.llim=FALSE))+
   ggsn::scalebar(north.mtbs, dist = 5, st.size=2.5, height=0.01, 
                  dist_unit="km", model = 'WGS84', transform=TRUE)+
   coord_sf()

north.map

```


1. Hayman Fire, CO (2003)

```{r fig.height=4, fig.width=3}
###MTBS
hayman.mtbs <- mtbs %>%
   filter(Event_ID == 'CO3922010528720020608')
###FIRED
hayman.fired <- fired %>% filter(id == 6161)
###Grab some info for the plot
burn_year <- '2002'
ig_date <- hayman.fired$ig_day
ig_day <- hayman.fired$ig_day
###Get the annual burn date raster
fire_dir <- paste(burnrasts, burn_year, "/", sep="")
###Find ranges and set up plot
modis_burn_dates <- 
   raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', burn_year, '.tif', sep=""))) %>%
   raster::crop(hayman.mtbs) %>%
   raster::mask(hayman.mtbs)
#Grab the range of burn days
range <- range(modis_burn_dates[], na.rm=TRUE)
start <- as.numeric(range[1])
breaks <- abs(range[1]-range[2])
# Update raster values to get "day since ignition"
modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)
# A function to plot our raster data
f1 <- rasterVis::levelplot(
   modis_burn_dates,
   par.settings = list(layout.heights=list(xlab.key.padding=1),
                       axis.line = list(col = "transparent"),
                       strip.background = list(col = 'transparent'),
                       strip.border = list(col = 'transparent')),
   margin=FALSE, region = TRUE,
   xlab = list(label = 'Days Since Ignition', cex = 1.5), 
   main = 'Hayman Fire, CO, 2002',
   scales = list(draw = FALSE),
   ylab=NULL,
   col.regions = colorRampPalette(brewer.pal(8, 'YlOrRd'))(breaks),
   colorkey = list(col = colorRampPalette(brewer.pal(8, 'YlOrRd'))(breaks), space="bottom")) +
   latticeExtra::layer(
      sp.polygons(as(hayman.mtbs, 'Spatial'), lwd = 1, scales=list(axes=FALSE)))
f1
```

Fire spread plot for the Hayman Fire, CO (2002)

```{r warning=F, fig.height=4, fig.width=3}
# MTBS
hayman.mtbs <- mtbs %>%
   filter(Event_ID == 'CO3922010528720020608')
# Filter the ztrax
ztrax.ext <- ztrax %>% filter(YearBuilt<=2002) %>%
   st_intersection(., hayman.mtbs)
# Filter the ICS-209s
hayman.ics <- inci209 %>% filter(INCIDENT_NAME=="HAYMAN" & START_YEAR==2002)
# Filter FIRED
hayman.fired <- fired %>% filter(id==6161)

# Grab some info for the plot
burn_year <- '2002'
ignition_date <- hayman.fired$ignition_date
ignition_day <- hayman.fired$ignition_day

###Get the annual burn date raster
fire.dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", burn_year, "/", sep="")

# Find ranges and set up plot
modis.dates <- raster::raster(
   file.path(paste(fire.dir, 'annual_burndate_y', burn_year, '.tif', sep=""))
) %>%
   raster::crop(hayman.mtbs) %>%
   raster::mask(hayman.mtbs)

#Grab the range of burn days
range <- range(modis.dates[],na.rm=TRUE)
start <- as.numeric(range[1])
breaks <- abs(range[1]-range[2])

#Update raster values to get "day since ignition"
modis.dates <- modis.dates - start
range <- range(modis.dates[],na.rm=TRUE)

#Extract as DF
modis.dates <- as.data.frame(modis.dates, xy = TRUE)

#Plot
hayman.map <- ggplot() +
   geom_raster(data = modis.dates , aes(x = x, y = y, fill=annual_burndate_y2002)) +
   scale_fill_fermenter(n.breaks=10, palette="Reds", na.value="white") +
   geom_sf(data=tubbs_fire_mtbs, fill="transparent", size=0.65)+
   geom_sf(data=ztrax_ext, color=alpha("black",0.1), size=0.5, size=0.75, shape=18, show.legend = TRUE)+
   labs(title="Tubbs Fire, CA (2017)",
        fill="Days Since Ignition")+
   theme_void()+
   theme(legend.position="bottom",
         plot.title = element_text(hjust = 0.5))+
   guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5,
                                 barwidth = 12, barheight = 0.5,
                                 ticks=FALSE, draw.llim=FALSE))+
   ggsn::scalebar(tubbs_fire_mtbs, dist = 2, st.size=3, height=0.01, 
                  dist_unit="km", model = 'WGS84', transform=TRUE)+
   coord_sf()

hayman.map
```


```{r tubbs}
###MTBS
tubbs_fire_mtbs <- mtbs %>%
  filter(Event_ID == 'CA3859812261820171009')

###ZTRAX
ztrax_ext <- ztrax %>% filter(YearBuilt<=2017)%>%
   st_intersection(., tubbs_fire_mtbs)

#FIRED
tubbs_fire_evt <- fired %>% filter(id==117157)

###Params
year <- '2017'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

###Tubbs fire example
modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
  raster::crop(tubbs_fire_mtbs) %>%
  raster::mask(tubbs_fire_mtbs)

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
start <- range[1]
breaks <- abs(range[1]-range[2])

#Update cells to be "days since ignition
modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

#Extract as DF
modis_burn_dates <- as.data.frame(modis_burn_dates, xy = TRUE)
#Plot
tubbs_fire_map <- ggplot() +
   geom_raster(data = modis_burn_dates , aes(x = x, y = y, fill=annual_burndate_y2017)) +
   scale_fill_fermenter(n.breaks=10, palette="Reds", na.value="white") +
   geom_sf(data=tubbs_fire_mtbs, fill="transparent", size=0.65)+
   geom_sf(data=ztrax_ext, color=alpha("black",0.1), size=0.5, size=0.75, shape=18, show.legend = TRUE)+
   labs(title="Tubbs Fire, CA (2017)",
        fill="Days Since Ignition")+
   theme_void()+
   theme(legend.position="bottom",
         plot.title = element_text(hjust = 0.5))+
   guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5,
                                 barwidth = 12, barheight = 0.5,
                                 ticks=FALSE, draw.llim=FALSE))+
   ggsn::scalebar(tubbs_fire_mtbs, dist = 2, st.size=3, height=0.01, 
                  dist_unit="km", model = 'WGS84', transform=TRUE)+
   coord_sf()

tubbs_fire_map
```


```{r camp}
#FIRED
camp_fire_evt <- fired%>%filter(id==124486)
ignition_date <- camp_fire_evt$ignition_date
last_date <- camp_fire_evt$last_date

#MTBS
camp_fire_mtbs <- mtbs %>%
   filter(Event_ID == 'CA3982012144020181108')

###ZTRAX
ztrax_ext <- ztrax %>% filter(YearBuilt<=2018) %>%
   st_intersection(., camp_fire_mtbs)
   
year <- '2018'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

# proj <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=1,1,-1,0,0,0,0 +units=m +no_defs"
modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(camp_fire_mtbs) %>%
   raster::mask(camp_fire_mtbs)

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])
end <- as.numeric(range[2])

modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

##Handle possible error dates
modis_burn_dates[modis_burn_dates>31] <- NA

#Extract as DF
modis_burn_dates <- as.data.frame(modis_burn_dates, xy = TRUE)
#Plot
camp_fire_map <- ggplot() +
   geom_raster(data = modis_burn_dates , aes(x = x, y = y, fill=annual_burndate_y2018)) +
   # scico::scale_fill_scico(palette = "lajolla", na.value="white", alpha=0.9,
   #                         breaks=seq(0,35,5), labels=c(0,5,10,15,20,25,30,35))+
   # scale_fill_distiller(palette = 'YlOrRd', direction=-2, breaks=seq(0,35,5),
   #                      na.value="white")+
   scale_fill_fermenter(n.breaks=10, palette="Reds", na.value="white") +
   geom_sf(data=camp_fire_mtbs, fill="transparent", size=0.65)+
   geom_sf(data=ztrax_ext, color=alpha("black",0.05), size=0.65, shape=18, show.legend = TRUE)+
   labs(title="Camp Fire, CA (2018)",
        fill="Days Since Ignition")+
   theme_void()+
   theme(legend.position="bottom",
         plot.title = element_text(hjust = 0.5))+
   guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5,
                                 barwidth = 12, barheight = 0.5,
                                 ticks=FALSE, draw.llim=FALSE))+
   ggsn::scalebar(camp_fire_mtbs, dist = 5, st.size=2.5, height=0.01, 
                  dist_unit="km", model = 'WGS84', transform=TRUE)+
   coord_sf()

camp_fire_map
```

```{r}
#FIRED
woolsey_fire_evt <- fired %>% filter(id==124525)
ignition_date <- camp_fire_evt$ignition_date
last_date <- camp_fire_evt$last_date

#MTBS
woolsey_fire_mtbs <- mtbs %>%
   filter(Event_ID == 'CA3424011870020181108')

###ZTRAX
ztrax_ext <- ztrax %>% filter(YearBuilt<=2018) %>%
   st_intersection(., woolsey_fire_mtbs)
   
year <- '2018'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

# proj <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=1,1,-1,0,0,0,0 +units=m +no_defs"
modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(woolsey_fire_mtbs) %>%
   raster::mask(woolsey_fire_mtbs)
plot(modis_burn_dates)

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])
end <- as.numeric(range[2])

modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

#Extract as DF
modis_burn_dates <- as.data.frame(modis_burn_dates, xy = TRUE)
#Plot
woolsey_fire_map <- ggplot() +
   geom_raster(data = modis_burn_dates , aes(x = x, y = y, fill=annual_burndate_y2018)) +
   # scico::scale_fill_scico(palette = "lajolla", na.value="white", alpha=0.9,
   #                         breaks=seq(0,35,5), labels=c(0,5,10,15,20,25,30,35))+
   # scale_fill_distiller(palette = 'YlOrRd', direction=-2, breaks=seq(0,35,5),
   #                      na.value="white")+
   scale_fill_fermenter(n.breaks=5, palette="Reds", na.value="white") +
   geom_sf(data=woolsey_fire_mtbs, fill="transparent", size=0.65)+
   geom_sf(data=ztrax_ext, color=alpha("black",0.1), size=0.65, shape=18, show.legend = TRUE)+
   labs(title="Woolsey Fire, CA (2018)",
        fill="Days Since Ignition")+
   theme_void()+
   theme(legend.position="bottom",
         plot.title = element_text(hjust = 0.5))+
   guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5,
                                 barwidth = 12, barheight = 0.5,
                                 ticks=FALSE, draw.llim=FALSE))+
   ggsn::scalebar(woolsey_fire_mtbs, dist = 5, st.size=2.5, height=0.01, 
                  dist_unit="km", model = 'WGS84', transform=TRUE)+
   coord_sf()

woolsey_fire_map
```



```{r king fire}
king_fire <- inci209 %>%
  filter(INCIDENT_ID == "2014_983669_KING")
# Create the spatial
king_fire_pt <- oks_fire %>%
  mutate(POO_LONGITUDE = ifelse(is.na(POO_LONGITUDE),0,as.numeric(POO_LONGITUDE)),
         POO_LATITUDE = ifelse(is.na(POO_LATITUDE),0,as.numeric(POO_LATITUDE))) %>%
  st_as_sf(., coords = c("POO_LONGITUDE", "POO_LATITUDE"),
                       crs = st_crs(conus)) %>%
  st_transform(crs = st_crs(conus))

king_fire_mtbs <- mtbs %>%
   filter(Event_ID == 'CA3878212060420140913')

#FIRED
king_fire_evt <- fired%>%filter(id==95950)

year <- '2014'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

###Hayman fire example
# proj <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=1,1,-1,0,0,0,0 +units=m +no_defs"
modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(king_fire_mtbs) %>%
   raster::mask(king_fire_mtbs)

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])

modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

# A function to plot our raster data
king_fire_map <- rasterVis::levelplot(modis_burn_dates,
                     par.settings = list(layout.heights=list(xlab.key.padding=1),
                                         axis.line = list(col = "transparent"),
                                         strip.background = list(col = 'transparent'),
                                         strip.border = list(col = 'transparent')),
                     margin=FALSE, region = TRUE,
                     xlab = list(label = 'Days Since Ignition', cex = 1.5), 
                     main = 'King Fire, CA, 2014',
                     scales = list(draw = FALSE),
                     ylab=NULL,
                     col.regions = colorRampPalette(brewer.pal(breaks, 'YlOrRd')),
                     colorkey = list(col = colorRampPalette(brewer.pal(breaks, 'YlOrRd')),
                                     space="bottom")) +
  latticeExtra::layer(sp.polygons(as(king_fire_mtbs, 'Spatial'), lwd = 1, scales=list(axes=FALSE)))

king_fire_map
```

```{r}
###MTBS
witch_fire_mtbs <- mtbs %>%
   filter(Event_ID == 'CA3307911676620071021')

###ZTRAX
ztrax_ext <- ztrax %>% filter(YearBuilt<=2007) %>%
   st_intersection(., witch_fire_mtbs)

dissolve <- st_union(witch_fire_mtbs)%>%st_sf()

#FIRED
witch_fire_evt <- fired%>%filter(id==46183)

year <- '2007'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

###Hayman fire example
# proj <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=1,1,-1,0,0,0,0 +units=m +no_defs"
modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(witch_fire_mtbs) %>%
   raster::mask(witch_fire_mtbs)

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])

modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

#Extract as DF
modis_burn_dates <- as.data.frame(modis_burn_dates, xy = TRUE)
#Plot
witch_fire_map <- ggplot() +
   geom_raster(data = modis_burn_dates , aes(x = x, y = y, fill=annual_burndate_y2007)) +
   # scico::scale_fill_scico(palette = "lajolla", na.value="white", alpha=0.9,
   #                         breaks=seq(0,35,5), labels=c(0,5,10,15,20,25,30,35))+
   # scale_fill_distiller(palette = 'YlOrRd', direction=-2, breaks=seq(0,35,5),
   #                      na.value="white")+
   scale_fill_fermenter(n.breaks=5, palette="Reds", na.value="white") +
   geom_sf(data=witch_fire_mtbs, fill="transparent", size=0.65)+
   geom_sf(data=ztrax_ext, color=alpha("black",0.1), size=0.5, shape=18, show.legend = TRUE)+
   labs(title="Witch-Poomacha Fire, CA (2007)",
        fill="Days Since Ignition")+
   theme_void()+
   theme(legend.position="bottom",
         plot.title = element_text(hjust = 0.5))+
   guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5,
                                 barwidth = 12, barheight = 0.5,
                                 ticks=FALSE, draw.llim=FALSE))+
   ggsn::scalebar(witch_fire_mtbs, dist = 5, st.size=2.5, height=0.01, 
                  dist_unit="km", model = 'WGS84', transform=TRUE)+
   coord_sf()

witch_fire_map
```


```{r}
cold_springs_cmplx <- nifc %>%
   filter(LocalIncid == "000594" |
          LocalIncid == "200130" |
          LocalIncid == "002144") %>%
   st_transform(crs = st_crs(mtbs))

dissolve <- st_union(cold_springs_cmplx)%>%st_sf()

###ZTRAX
ztrax_ext <- ztrax %>% filter(YearBuilt<=2020) %>%
   st_intersection(., dissolve)

year <- '2020'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(dissolve) %>%
   raster::mask(dissolve)

modis_burn_dates[modis_burn_dates<245] <- NA

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])

modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)

#Extract as DF
modis_burn_dates <- as.data.frame(modis_burn_dates, xy = TRUE)
#Plot
cold_springs_cmplx_map <- ggplot() +
   geom_raster(data = modis_burn_dates , aes(x = x, y = y, fill=annual_burndate_y2020)) +
   # scico::scale_fill_scico(palette = "lajolla", na.value="white", alpha=0.9,
   #                         breaks=seq(0,35,5), labels=c(0,5,10,15,20,25,30,35))+
   # scale_fill_distiller(palette = 'YlOrRd', direction=-2, breaks=seq(0,35,5),
   #                      na.value="white")+
   scale_fill_fermenter(n.breaks=5, palette="Reds", na.value="white") +
   geom_sf(data=cold_springs_cmplx, fill="transparent", size=0.65)+
   geom_sf(data=ztrax_ext, color=alpha("black",0.2), size=0.65, shape=18, show.legend = TRUE)+
   labs(title="Cold Springs Complex Fire, WA (2020)",
        fill="Days Since Ignition")+
   theme_void()+
   theme(legend.position="bottom",
         plot.title = element_text(hjust = 0.5))+
   guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5,
                                 barwidth = 12, barheight = 0.5,
                                 ticks=FALSE, draw.llim=FALSE))+
   ggsn::scalebar(dissolve, dist = 10, st.size=2.5, height=0.01, 
                  dist_unit="km", model = 'WGS84', transform=TRUE,
                  location="bottomleft")+
   coord_sf()

cold_springs_cmplx_map
```

```{r}
claremont_bear <- nifc %>%
   filter(LocalIncid == "001308") %>%
   st_transform(crs = st_crs(mtbs))

###ZTRAX
ztrax_ext <- ztrax %>% filter(YearBuilt<=2020) %>%
   st_intersection(., claremont_bear)

year <- '2020'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(claremont_bear) %>%
   raster::mask(claremont_bear)

##Handle possible error dates
modis_burn_dates[modis_burn_dates>279] <- NA

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])

modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])

#Extract as DF
modis_burn_dates <- as.data.frame(modis_burn_dates, xy = TRUE)
#Plot
claremont_bear_map <- ggplot() +
   geom_raster(data = modis_burn_dates , aes(x = x, y = y, fill=annual_burndate_y2020)) +
   # scico::scale_fill_scico(palette = "lajolla", na.value="white", alpha=0.9,
   #                         breaks=seq(0,35,5), labels=c(0,5,10,15,20,25,30,35))+
   # scale_fill_distiller(palette = 'YlOrRd', direction=-2, breaks=seq(0,60,10),
   #                      na.value="white")+
   scale_fill_fermenter(n.breaks=8, palette="Reds", na.value="white") +
   geom_sf(data=claremont_bear, fill="transparent", size=0.65)+
   geom_sf(data=ztrax_ext, color=alpha("black",0.25), size=0.75, shape=18, show.legend = TRUE)+
   labs(title="Claremont-Bear Fire, CA (2020)",
        fill="Days Since Ignition")+
   theme_void()+
   theme(legend.position="bottom",
         plot.title = element_text(hjust = 0.5))+
   guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5,
                                 barwidth = 12, barheight = 0.5,
                                 ticks=FALSE, draw.llim=FALSE))+
   ggsn::scalebar(claremont_bear, dist = 10, st.size=2.5, height=0.01, 
                  dist_unit="km", model = 'WGS84', transform=TRUE)+
   coord_sf()

claremont_bear_map

```

```{r}
august_cmplx <- nifc %>%
   filter(LocalIncid == "000753") %>%
   st_transform(crs = st_crs(mtbs))

###ZTRAX
ztrax_ext <- ztrax %>% filter(YearBuilt<=2020) %>%
   st_intersection(., august_cmplx)

year <- '2020'
fire_dir <- paste("C:/Users/mccoo/OneDrive/mcook/fast-fires/data/burndate/", year, "/", sep="")

modis_burn_dates <- raster::raster(file.path(paste(fire_dir, 'annual_burndate_y', year, '.tif', sep=""))) %>%
   raster::crop(august_cmplx) %>%
   raster::mask(august_cmplx)

#Grab the range of burn days
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])
start <- as.numeric(range[1])

modis_burn_dates <- modis_burn_dates - start
range <- range(modis_burn_dates[],na.rm=TRUE)
breaks <- abs(range[1]-range[2])

#Extract as DF
modis_burn_dates <- as.data.frame(modis_burn_dates, xy = TRUE)
#Plot
august_cmplx_map <- ggplot() +
   geom_raster(data = modis_burn_dates , aes(x = x, y = y, fill=annual_burndate_y2020)) +
   # scico::scale_fill_scico(palette = "lajolla", na.value="white", alpha=0.9,
   #                         breaks=seq(0,35,5), labels=c(0,5,10,15,20,25,30,35))+
   # scale_fill_distiller(palette = 'YlOrRd', direction=-2, breaks=seq(0,70,10),
   #                      na.value="white")+
   scale_fill_fermenter(n.breaks=10, palette="Reds", na.value="white") +
   geom_sf(data=august_cmplx, fill="transparent", size=0.65)+
   geom_sf(data=ztrax_ext, color=alpha("black",0.3), size=1, shape=18, show.legend = TRUE)+
   labs(title="August Complex Fire, CA (2020)",
        fill="Days Since Ignition")+
   theme_void()+
   theme(legend.position="bottom",
         plot.title = element_text(hjust = 0.5))+
   guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5,
                                 barwidth = 12, barheight = 0.5,
                                 ticks=FALSE, draw.llim=FALSE))+
   ggsn::scalebar(august_cmplx, dist = 10, st.size=2.5, height=0.01, 
                  dist_unit="km", model = 'WGS84', transform=TRUE)+
   coord_sf()

august_cmplx_map

```

# Panel figure

```{r, fig.width=10, fig.height=6, warning=False}
ggarrange(hayman_fire_map, witch_fire_map, oks_fire_map, camp_fire_map, claremont_bear_map, cold_springs_cmplx_map,
          common.legend = TRUE, legend="bottom", nrow = 2, ncol = 3)+
   theme(plot.margin = unit(c(1.2,1.2,1.2,1.2), "lines"))

# ggarrange(hayman_fire_map, witch_fire_map, oks_fire_map, 
#           tubbs_fire_map, camp_fire_map, woolsey_fire_map, 
#           august_cmplx_map, claremont_bear_map, cold_springs_cmplx_map,
#           common.legend = TRUE, legend="bottom", nrow = 3, ncol = 3)+
#    theme(plot.margin = unit(c(1,1,1,1), "lines"))

# grid.arrange(hayman_fire_map, witch_fire_map, oks_fire_map, 
#              camp_fire_map, august_cmplx_map, cold_springs_cmplx_map,
#              ncol=3, nrow=2)

# library(latticeExtra)
# c(camp_fire_map, hayman_fire_map, tubbs_fire_map, 
#   oks_fire_map, cold_springs_cmplx_map, claremont_bear_map)

# cowplot::plot_grid(camp_fire_map, hayman_fire_map, tubbs_fire_map, 
#                    oks_fire_map, cold_springs_cmplx_map, claremont_bear_map,
#                    align = "v", ncol = 3, rel_heights = c(1/4, 1/4, 1/4))
```

```{r, fig.width=10, fig.height=9, warning=False}
grid.arrange(hayman_fire_map, witch_fire_map, oks_fire_map, 
             tubbs_fire_map, camp_fire_map, woolsey_fire_map,
             august_cmplx_map, cold_springs_cmplx_map, claremont_bear_map,
             ncol=3, nrow=3)
```

# Plot BUPR sum through burn days

## Here, we will test various methods for temporal autocorrelation between burn area and housing density. We will also test the relationship between maximum growth and maximum housing density.

```{r, fig.caption="Test"}
###Create daily fired subset
#####Let's take an example fire, the Rim Fire in CA
ex <- daily %>% filter(id==57206) %>%
   #daily hectares
   mutate(daily_area_ha = daily_area_km2*100)

###Create a simple time-series plot
p1 <- ggplot(ex)+
   geom_line(aes(date, daily_area_km2), na.rm=TRUE)+
   xlab("")+
   ylab("Daily Growth (km2)")+
   scale_x_date(breaks=date_breaks("5 days"),
                labels=date_format("%b %d"))+
   theme_light()
p2 <- ggplot(ex, aes(date, bupr_sum))+
   geom_bar(stat="identity")+
   xlab("Burn Date")+
   ylab("Built-up Property Records")+
   scale_x_date(breaks=date_breaks("5 days"),
                labels=date_format("%b %d"))+
   theme_light()

arr <- ggarrange(p1, p2, nrow = 2, ncol = 1)

annotate_figure(arr, top="Daily Burn Area and Property Density for the Rim Fire, CA")

```

